Spatial modelling of the electoral two-party preferred vote in Australia. A study of federal elections between 2001 and 2016 via the `eechidna` `R` package.

### 2019-03-31 draft-paper.Rmd
fixed variable names. draft 1 complete and ready for review.

# Order electorates in alphabetical order to match spatial matrix
model_df <- small_df %>% 
  arrange(year, DivisionNm) %>% 
  dplyr::select(order(colnames(.))) %>% 
  rename(ManagerAdmin = ManagerAdminClericalSales, 
    OtherLanguage = OtherLanguageHome,
    Born_SE_EU = Born_SE_Europe)
```

@@

```{r prepplot, include = F}
p1 <- grid_visreg("Incomes", top = T)
p2 <- grid_visreg("Unemployment")
p3 <- grid_visreg("Extractive")
p4 <- grid_visreg("Transformative")
p5 <- grid_visreg("ManagerAdmin")
p6 <- grid_visreg("DiffAddress")
p7 <- grid_visreg("DeFacto", top = T)
p8 <- grid_visreg("MedianAge")
p9 <- grid_visreg("Education")
p10 <- grid_visreg("OtherLanguage")
p11 <- grid_visreg("Born_SE_EU")
p12 <- grid_visreg("Born_Asia")
p13 <- grid_visreg("Judaism")
```

>>>>

# Order electorates in alphabetical order to match spatial matrix
model_df <- small_df %>% 
  arrange(year, DivisionNm) %>% 
  dplyr::select(order(colnames(.))) %>% 
  rename(ManagerAdmin = ManagerAdminClericalSales, 
    OtherLanguage = OtherLanguageHome,
    BornSEEuro = BornSEEurope,
    BornAsia = Born_Asia)
```

@@

```{r prepplot, include = F}
p1 <- grid_visreg("Incomes", top = T)
p2 <- grid_visreg("Unemployment")
p3 <- grid_visreg("Extractive")
p4 <- grid_visreg("Transformative")
p5 <- grid_visreg("ManagerAdmin")
p6 <- grid_visreg("DiffAddress")
p7 <- grid_visreg("DeFacto", top = T)
p8 <- grid_visreg("MedianAge")
p9 <- grid_visreg("Education")
p10 <- grid_visreg("OtherLanguage")
p11 <- grid_visreg("BornSEEuro")
p12 <- grid_visreg("BornAsia")
p13 <- grid_visreg("Judaism")
```
